---
title: "Effect of Prenatal Androgenization on Spontaneous Firing of Arcuate KNDy Neurons"
author: "Amanda Gibson"
date: '2021-06-01'
output:
  word_document: 
    toc: yes
  html_notebook: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
# options(digits=3)
```

```{r callSetUp, message=FALSE, warning=FALSE}
# # Set-up
# The `AG_KNDyPNA_setup.R` file reads the .REnviron to load the appropriate files for the local computer. It also calls the appropriate libraries and sources the other function files to be used for analysis.
# 
# This file also loads the `KNDy_mouse_demo`, `KNDy_cells`, `KNDy_exclude`, `KNDy_firingRate`, `KNDy_cycles`, and other dataframes by reading the `KNDyPNA_Data` excel file.
#This runs the setup script that loads the appropriate libraries and files
source("./Scripts/AG_KNDyPNA_setup.R")

library(flextable)
doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
# doc.type = "docx"
```

```{r ppt-setUp}
#create a new powerpoint
KNDy_PPT = read_pptx()

#add a new title slide
KNDy_PPT = add_slide(KNDy_PPT, layout = "Title Slide", master = "Office Theme")

#Write "KNDy - PNA DATA" in the title slot
KNDy_PPT = ph_with(KNDy_PPT, value = "KNDy - PNA Data", location = ph_location_label(ph_label = "Title 1"))

#view the possible layout properties 
#layout_properties(x = KNDy_PPT, layout = "Title Slide")

# Save plots
save = FALSE
toPPT = TRUE
ppt = KNDy_PPT

```


```{r Get-Data-Ready}

# ## Get Data Ready
# 
# The `GetDataReadyFunc` function takes the `KNDy_mouse_demo` and `KNDy_cells` data frame to produce a combined `KNDyDATA` data frame.
# 
# This does the following transformations
# 
# * reformats the columns with dates into date format
# * Creates a new variable Sac_9plus that is TRUE when the time of sacrifice is more than 9hr after lights on
# * Creates a new variable AgeGroup that is TRUE when the mouse is a juvenile
# * Creates a new variable Quiet that is TRUE when the spontaneous average firing rate is less than a cutoff value
# cutoff value is specified by rateForQuiet
# * Creates a new variable TreatxAge to generate four groups 
#   + PNA - Adult
#   + PNA - Juvenile
#   + Control - Adult
#   + Control - Juvenile
# * Makes AgeGroup a factor, and gives it nice labels, Juvenile or Adult
# * Gets rid of white space in the "Who" variable
# * Makes Treatment a factor variable with orders "Main Colony Control", "Control", "Vehicle", "DHT"
# * Combines the KNDy_exclude information
# *Readjusts the order of variables within the KNDyDATA data frame to be a little more helpful.  
# 
# If the order of the excel sheet changes, this function has to change

allDFs <- GetDataReadyFunc(
  KNDy_mouse_demo, 
  KNDy_cells, 
  KNDy_exclude, 
  KNDy_firingRate, 
  KNDy_burstData, 
  KNDy_clusterData, 
  rateForQuiet, 
  KNDy_TimingData
  )

KNDyDATA <-  allDFs$KNDyDATA
KNDy_mouse_demo <- allDFs$KNDy_mouse_demo
KNDy_cells <- allDFs$KNDy_cells
KNDy_firingRate <- allDFs$KNDy_firingRate
VBW_BurstsPerHour <- allDFs$VBW_BurstsPerHour
VBW_BurstsPerHour_hour1 <- allDFs$VBW_BurstsPerHour_hour1

#Store the dataframes as excel sheets
KNDyAnalysisWB = createWorkbook()
```

```{r KNDy_VarNames}
# Creates the KNDy_VarNames data frame with the nice names for each variable
# Creates the following lists or expressions of variable groups. 
# There is a _quo which is quoted for each variable, or the basename version which is the exprs (expressions) list
# 
# - timingVars
# - demoVarsAll
# - BurstVars_spont
# - numPeaksVars
# - numNadirsVars
# - meanPeakDurVars
# - meanNadirDurVars
# - totalPeakDurVars
# - totalNadirDurVars
# - meanPeakFiringVars
# - meanNadirFiringVars
# - allClusterVars
# - cluster2x2SD_Vars
# - cluster3x3SD_Vars
# - cluster 2x2SE_Vars
# - cluster 3x3SE_Vars

KNDy_VarNames <- KNDy_varNamesFunc(KNDyDATA)
```

```{r}

# if(doc.type == "docx"){flextable(df)} else {df}
```

# Filtering Information
For this report, cells were not filtered by recording duration. Mice that were up to 160 days of age were included. Uterine mass up to 110 mg was included. There was no filtering of the dataset by order of cell recorded or order of mice recorded from one litter. Only cells that Amanda recorded were included, but this includes cells that were from animals that Jenn sliced. This dataset does not include main colony control mice, which therefore also excludes homozygous mice. Cells that had other technical reasons for exclusion are not included in this dataset.

```{r}
# Change this list to change how the dataset is filtered
# This just needs to be changed here, and then it can be applied throughout
minDuration = NA
maxAgeInDays = 160
maxUterineMass = 110
cellNums = levels(KNDyDATA$CellNum)
mouseNums = levels(KNDyDATA$MouseNum)
whoRecorded = "Amanda"
whoSliced = levels(KNDyDATA$Who)
includeMainCol = FALSE
includeHomozygous = FALSE
excludeMarkedCells = TRUE


filterParams = list(
  excludeMarkedCells = excludeMarkedCells,
  minDuration = minDuration,
  maxAgeInDays = maxAgeInDays,
  maxUterineMass = maxUterineMass,
  cellNums = cellNums,
  mouseNums = mouseNums,
  whoRecorded = whoRecorded,
  whoSliced = whoSliced,
  includeMainCol = includeMainCol,
  includeHomozygous = includeHomozygous
)

burstParameters <- exprs(
  tf,
  bf,
  mbd,
  spb,
  intra,
  ssf,
  inter
)

binWidths <- list(
  tf = 0.04,
  bf = 0.007,
  mbd = NA,
  spb = NA,
  intra = NA,
  ssf = 0.02,
  inter = NA
)

dotSizes <- list(
  tf = 3,
  bf = 3,
  mbd = 1,
  spb = 1,
  intra = 1,
  ssf = 3,
  inter = 1
)

groupingVars <- exprs(AgeGroup, GenTreatment)
rateForQuiet <- 0.005
```


```{r}
# Full Spontaneous - 210 burst window
bParams_spont_0.21 <- loadBurstParamsData_noFilters(
  analysis = "spont_0.21",
  BurstOutputsFolder = file.path(BurstOutputsFolder, "allCells"),
  demoDF = KNDyDATA
)

bParams_spont_0.21 <- do.call(
  filterData_options,
  c(
    list(df = bParams_spont_0.21),
    filterParams
  )
)

bParams_spont_0.21_grouped <- bParams_spont_0.21 %>%
  group_by(
    !!! groupingVars
  )
```

```{r}
# 0-20 min Spontaneous - 210 burst window
bParams_spont_0_20_0.21 <- loadBurstParamsData_noFilters(
  analysis = "spont_bin20_0_0.21",
  BurstOutputsFolder = file.path(BurstOutputsFolder, "allCells"),
  demoDF = KNDyDATA
)

bParams_spont_0_20_0.21 <- do.call(
  filterData_options,
  c(
    list(df = bParams_spont_0_20_0.21),
    filterParams
  )
)

bParams_spont_0_20_0.21_grouped <- bParams_spont_0_20_0.21 %>%
  group_by(
    !!! groupingVars
  )
```

```{r}
# 20-40 min Spontaneous - 210 burst window
bParams_spont_20_40_0.21 <- loadBurstParamsData_noFilters(
  analysis = "spont_bin20_1_0.21",
  BurstOutputsFolder = file.path(BurstOutputsFolder, "allCells"),
  demoDF = KNDyDATA
)

bParams_spont_20_40_0.21 <- do.call(
  filterData_options,
  c(
    list(df = bParams_spont_20_40_0.21),
    filterParams
  )
)

bParams_spont_20_40_0.21_grouped <- bParams_spont_20_40_0.21 %>%
  group_by(
    !!! groupingVars
  )
```

```{r}
# 40-60 min Spontaneous - 210 burst window
bParams_spont_40_60_0.21 <- loadBurstParamsData_noFilters(
  analysis = "spont_bin20_2_0.21",
  BurstOutputsFolder = file.path(BurstOutputsFolder, "allCells"),
  demoDF = KNDyDATA
)

bParams_spont_40_60_0.21 <- do.call(
  filterData_options,
  c(
    list(df = bParams_spont_40_60_0.21),
    filterParams
  )
)

bParams_spont_40_60_0.21_grouped <- bParams_spont_40_60_0.21 %>%
  group_by(
    !!! groupingVars
  )
```

# Full Spontaneous Recordings 

## Burst Window 210 ms - peak of control animals
```{r}
df <- bParams_spont_0.21
df_grouped <- bParams_spont_0.21_grouped
df_contrasts <- makeTreatandAgeContrasts(bParams_spont_0.21)

df_0_20 <- bParams_spont_0_20_0.21
df_20_40 <- bParams_spont_20_40_0.21
df_40_60 <- bParams_spont_40_60_0.21
```

### Counts

```{r}
countSum <- countLittersCellsFiringBursting(
  df_grouped,
  groupingVars,
  rateForQuiet
)

if(doc.type == "docx"){
  formatCountTableForPPT(
    countSum,
    fontSize = 10
  )
} else {countSum}
```



```{r eval=FALSE, include=FALSE}
#overwhelming
meanSum_spont_0.21 <- map_df(
  burstParameters,
  doMeanSummaryForColumn,
  df = bParams_spont_0.21_grouped,
  includeVarInColName = FALSE,
  addVarCol = TRUE,
  niceNames = KNDy_VarNames
)
```

### Total Frequency
```{r}
param = expr(tf)
```

#### Mean Data - tf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -tf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {quartileSum}
```

#### ANOVA -tf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot -tf
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Burst Frequency
```{r}
param = expr(bf)
```

#### Mean Data -bf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -bf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA - bf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```





#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Mean Burst Duration
```{r}
param = expr(mbd)
```

#### Mean Data - mbd

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -mbd

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -mbd

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Spikes Per Burst
```{r}
param = expr(spb)
```

#### Mean Data -spb

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -spb

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -spb

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Intra-burst Interval
```{r}
param = expr(intra)
```

#### Mean Data -intra

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -intra

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -intra

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Single Spike Frequency
```{r}
param = expr(ssf)
```

#### Mean Data -ssf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -ssf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -ssf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Inter-event Interval
```{r}
param = expr(inter)
```

#### Mean Data -inter

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -inter

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -inter

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

# First 20 Min of Spontaneous

## Burst Window 210 ms - peak of control animals
```{r}
df <- bParams_spont_0_20_0.21
df_grouped <- bParams_spont_0_20_0.21_grouped
df_contrasts <- makeTreatandAgeContrasts(bParams_spont_0_20_0.21)
```

### Counts

```{r}
countSum <- countLittersCellsFiringBursting(
  df_grouped,
  groupingVars,
  rateForQuiet
)

if(doc.type == "docx"){
  formatCountTableForPPT(
    countSum,
    fontSize = 10
  )
} else {countSum}
```


### Total Frequency
```{r}
param = expr(tf)
```

#### Mean Data - tf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -tf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {quartileSum}
```

#### ANOVA -tf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot -tf
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Burst Frequency
```{r}
param = expr(bf)
```

#### Mean Data -bf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -bf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA - bf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Mean Burst Duration
```{r}
param = expr(mbd)
```

#### Mean Data - mbd

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -mbd

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -mbd

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Spikes Per Burst
```{r}
param = expr(spb)
```

#### Mean Data -spb

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -spb

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -spb

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Intra-burst Interval
```{r}
param = expr(intra)
```

#### Mean Data -intra

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -intra

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -intra

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Single Spike Frequency
```{r}
param = expr(ssf)
```

#### Mean Data -ssf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -ssf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -ssf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Inter-event Interval
```{r}
param = expr(inter)
```

#### Mean Data -inter

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -inter

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -inter

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

# 20-40 min of Spontaneous

## Burst Window 210 ms - peak of control animals
```{r}
df <- bParams_spont_20_40_0.21
df_grouped <- bParams_spont_20_40_0.21_grouped
df_contrasts <- makeTreatandAgeContrasts(bParams_spont_20_40_0.21)
```

### Counts

```{r}
countSum <- countLittersCellsFiringBursting(
  df_grouped,
  groupingVars,
  rateForQuiet
)

if(doc.type == "docx"){
  formatCountTableForPPT(
    countSum,
    fontSize = 10
  )
} else {countSum}
```


### Total Frequency
```{r}
param = expr(tf)
```

#### Mean Data - tf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -tf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {quartileSum}
```

#### ANOVA -tf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot -tf
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Burst Frequency
```{r}
param = expr(bf)
```

#### Mean Data -bf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -bf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA - bf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Mean Burst Duration
```{r}
param = expr(mbd)
```

#### Mean Data - mbd

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -mbd

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -mbd

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Spikes Per Burst
```{r}
param = expr(spb)
```

#### Mean Data -spb

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -spb

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -spb

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Intra-burst Interval
```{r}
param = expr(intra)
```

#### Mean Data -intra

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -intra

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -intra

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Single Spike Frequency
```{r}
param = expr(ssf)
```

#### Mean Data -ssf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -ssf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -ssf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Inter-event Interval
```{r}
param = expr(inter)
```

#### Mean Data -inter

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -inter

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -inter

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

# 40-60 Min of Spontaneous

## Burst Window 210 ms - peak of control animals
```{r}
df <- bParams_spont_40_60_0.21
df_grouped <- bParams_spont_40_60_0.21_grouped
df_contrasts <- makeTreatandAgeContrasts(bParams_spont_40_60_0.21)
```

### Counts

```{r}
countSum <- countLittersCellsFiringBursting(
  df_grouped,
  groupingVars,
  rateForQuiet
)

if(doc.type == "docx"){
  formatCountTableForPPT(
    countSum,
    fontSize = 10
  )
} else {countSum}
```


### Total Frequency
```{r}
param = expr(tf)
```

#### Mean Data - tf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -tf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {quartileSum}
```

#### ANOVA -tf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot -tf
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Burst Frequency
```{r}
param = expr(bf)
```

#### Mean Data -bf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -bf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA - bf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Mean Burst Duration
```{r}
param = expr(mbd)
```

#### Mean Data - mbd

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -mbd

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -mbd

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Spikes Per Burst
```{r}
param = expr(spb)
```

#### Mean Data -spb

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -spb

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -spb

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```


#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Intra-burst Interval
```{r}
param = expr(intra)
```

#### Mean Data -intra

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -intra

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -intra

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Single Spike Frequency
```{r}
param = expr(ssf)
```

#### Mean Data -ssf

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -ssf

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -ssf

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```

### Inter-event Interval
```{r}
param = expr(inter)
```

#### Mean Data -inter

```{r}

meanSum <- doMeanSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatMeanSummaryTableForPPT(
    meanSum, 
    fontSize = 12
  )
} else {meanSum}

```

#### Quartile Data -inter

```{r}
quartileSum <- doQuartileSummaryForColumn(
  param,
  df = df_grouped,
  includeVarInColName = FALSE,
  addVarCol = FALSE,
  niceNames = KNDy_VarNames
)

if(doc.type == "docx"){
  formatQuartileSummaryTableForPPT(
    quartileSum, 
    fontSize = 12
  )
} else {meanSum}
```

#### ANOVA -inter

```{r}
Model <- lm_byTreatxAge(param, df_contrasts)
        

if(doc.type == "docx"){
  ANOVA_out <- makePlainANOVA_getVals_treatAge(Model)
  formatANOVAforPPT(
    ANOVA_out$ANOVA,
    fontSize = 18
  )
} else {
  ANOVA_table <- makeANOVA_TreatAge(Model)
  ANOVA_table %>%
    kable_styling(
      font_size = 18,
      bootstrap_options = c("striped"), full_width = TRUE
    )
}
```




#### Plot
```{r}
viz <- plotBurstParamBox(
  df,
  param
)
viz
```

```{r}
param_overTime <- combineBurstBinsForParam(
    df_0_20,
    df_20_40,
    df_40_60,
    param
  )
  
viz <- plotBurstParamBox_overTime(
  param,
  param_overTime
)
viz
```
