---
title: Analysis of Prenatal Androgenization Effects on Extracellular Firing of KNDy
  Neurons
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Set-up
The `AG_KNDyPNA_setup.R` file reads the .REnviron to load the appropriate files for the local computer. It also calls the appropriate libraries and sources the other function files to be used for analysis.

This file also loads the `KNDy_mouse_demo`, `KNDy_cells`, `KNDy_exclude`, `KNDy_firingRate`, and `KNDy_cycles` dataframes by reading the `KNDyPNA_Data` excel file.
```{r callSetUp, message=FALSE, warning=FALSE}
#This runs the setup script that loads the appropriate librarys and files
source("./Scripts/AG_KNDyPNA_setup.R")
```

## Get Data Ready

The `GetDataReadyFunc` function takes the `KNDy_mouse_demo` and `KNDy_cells` data frame to produce a combined `KNDyDATA` data frame.

This does the following transformations

* reformats the columns with dates into date format
* Creates a new variable Sac_9plus that is TRUE when the time of sacrifice is more than 9hr after lights on
* Creates a new variable AgeGroup that is TRUE when the mouse is a juvenile
* Creates a new variable Quiet that is TRUE when the spontaneous average firing rate is less than a cutoff value
cutoff value is specified by rateForQuiet
* Creates a new variable TreatxAge to generate four groups 
  + PNA - Adult
  + PNA - Juvenile
  + Control - Adult
  + Control - Juvenile
* Makes AgeGroup a factor, and gives it nice labels, Juvenile or Adult
* Gets rid of white space in the "Who" variable
* Makes Treatment a factor variable with orders "Main Colony Control", "Control", "Vehicle", "DHT"
* Combines the KNDy_exclude information
*Readjusts the order of variables within the KNDyDATA data frame to be a little more helpful.  

If the order of the excel sheet changes, this function has to change
```{r Get-Data-Ready}
allDFs <- GetDataReadyFunc(KNDy_mouse_demo, KNDy_cells, KNDy_exclude, KNDy_firingRate, rateForQuiet)

KNDyDATA <-  allDFs$KNDyDATA
KNDy_mouse_demo <- allDFs$KNDy_mouse_demo
KNDy_cells <- allDFs$KNDy_cells
KNDy_firingRate <- allDFs$KNDy_firingRate
```

```{r KNDy_VarNames}
# Creates the KNDy_VarNames data frame with the nice names for each variable
# Creates the following lists or expressions of variable groups. 
# There is a _quo which is quoted for each variable, or the basename version which is the exprs (expressions) list
# 
# - timingVars
# - demoVarsAll
# - BurstVars_spont
# - numPeaksVars
# - numNadirsVars
# - meanPeakDurVars
# - meanNadirDurVars
# - totalPeakDurVars
# - totalNadirDurVars
# - meanPeakFiringVars
# - meanNadirFiringVars
# - allClusterVars
# - cluster2x2SD_Vars
# - cluster3x3SD_Vars
# - cluster 2x2SE_Vars
# - cluster 3x3SE_Vars

KNDy_VarNames <- KNDy_varNamesFunc(KNDyDATA)
```

# `KNDyDATA`
```{r KNDyDATA}
KNDyDATA
```
  
The KNDyDATA dataframe can be separated into the adult recordings and the juvenile recordings
```{r separate-by-age-KNDyDATA}
#create dataframes with only juvenile recordings and only adult recordings
sepDFs <- sep_by_age(KNDyDATA)
KNDyDATA_juv <- sepDFs$df_juv
KNDyDATA_adult <- sepDFs$df_adult
```

## `KNDyDATA_juv`
```{r KNDyDATA_juv}
KNDyDATA_juv
```

## `KNDyDATA_adult`
```{r KNDyDATA_adult}
KNDyDATA_adult
```

# Number of Cells

This excludes the cells that have been marked for exclusion  
<em><span style="color:red">Note that the adult cage numbers have to be updated. Not all of the adults came from the same litters</span></em>
```{r Count-Cells}
#Determine which df you want you use 
df = excludeFunc(KNDyDATA) #exclude
#df = KNDyDATA #include all

KNDy_count = df %>%
  select( #select only these columns
    CellID,
    MouseID,
    Cage,
    GenTreatment,
    AgeGroup,
    Who
  )%>%
  group_by(Who, GenTreatment, AgeGroup)%>% #group by the treatment by age variable
  summarise(
    numCells= n(), #count the number of data points for each group
    numMice = length(unique(MouseID)), #count the number of unique MouseIDs
    numLitters = length(unique(Cage)), #Count the number of unique cage numbers
    .groups = 'drop')
KNDy_count

numCells_Jenn_Con_Juv <- with(KNDy_count, numCells[Who == "Jenn" & GenTreatment == "Control" & AgeGroup == "Juvenile"])
numCells_Jenn_PNA_Juv <- with(KNDy_count, numCells[Who == "Jenn" & GenTreatment == "PNA" & AgeGroup == "Juvenile"])
numCells_Amanda_Con_Juv <- with(KNDy_count, numCells[Who == "Amanda" & GenTreatment == "Control" & AgeGroup == "Juvenile"])
numCells_Amanda_PNA_Juv <- with(KNDy_count, numCells[Who == "Amanda" & GenTreatment == "PNA" & AgeGroup == "Juvenile"])
numCells_Amanda_Con_Adult <- with(KNDy_count, numCells[Who == "Amanda" & GenTreatment == "Control" & AgeGroup == "Adult"])
numCells_Amanda_PNA_Adult <- with(KNDy_count, numCells[Who == "Amanda" & GenTreatment == "PNA" & AgeGroup == "Adult"])
```

Jenn recorded `r numCells_Jenn_Con_Juv` cells from control juvenile mice. She recorded `r numCells_Jenn_PNA_Juv` cells from PNA juvenile mice. Amanda recorded `r numCells_Amanda_Con_Juv` cells from control juvenile mice and `r numCells_Amanda_PNA_Juv` PNA juvenile cells. She recorded `r numCells_Amanda_Con_Adult` cells from control adult mice and `r numCells_Amanda_PNA_Adult` cells from PNA adult mice.  

# PNA Phenotype
These are the measurements from the surviving littermaters of the juveniles that were recorded.  
<em><span style="color:red">Amanda will need to go back through her old data to pull out the cycling data for the adults.</span></em> 

<em><span style="color:red">pull in AGD</span></em>

## Cycles
```{r Cycles-calc}
KNDy_cycles_long <- make_cycles_long(KNDy_cycles) %>%
  add_Day_col() %>%
  drop_na(Stage)

#Control
KNDy_cycles_control <- KNDy_cycles_long %>%
  filter(GenTreatment == "Control") %>%
  cyclesPlotFunc()

#PNA
KNDy_cycles_PNA <- KNDy_cycles_long %>%
  filter(GenTreatment == "PNA") %>%
  cyclesPlotFunc()
```

### Control
```{r}
KNDy_cycles_control
```

### PNA
```{r PNA-cycles}
KNDy_cycles_PNA
```


# `KNDy_firingRate`
```{r}
KNDy_firingRate
```
```{r}
KNDy_firingRate_long <- KNDy_firingRate %>%
  excludeFunc() %>%
  make_firing_long

KNDy_firingRate_long <- KNDy_firingRate_long %>%
  add_Min_col()

# Uncomment to print, but 6000+ rows
# KNDy_firingRate_long

# Adults
KNDy_firingRate_Adult_Con_plot <- KNDy_firingRate_long %>%
  excludeFunc() %>%
  filter(AgeGroup == "Adult" & GenTreatment == "Control") %>%
  firingRatePlotFunc()

KNDy_firingRate_Adult_PNA_plot <- KNDy_firingRate_long %>%
  excludeFunc() %>%
  filter(AgeGroup == "Adult" & GenTreatment == "PNA") %>%
  firingRatePlotFunc()

# Juveniles
KNDy_firingRate_Juv_Con_plot <- KNDy_firingRate_long %>%
  excludeFunc() %>%
  filter(AgeGroup == "Juvenile" & GenTreatment == "Control") %>%
  firingRatePlotFunc()

KNDy_firingRate_Juv_PNA_plot <- KNDy_firingRate_long %>%
  excludeFunc() %>%
  filter(AgeGroup == "Juvenile" & GenTreatment == "PNA") %>%
  firingRatePlotFunc()
```

The KNDy_firingRate dataframe can be separated into the adult recordings and the juvenile recordings
```{r separate-by-age-firingRate}
#create dataframes with only juvenile recordings and only adult recordings
sepDFs <- sep_by_age(KNDy_firingRate)
KNDy_firingRate_juv <- sepDFs$df_juv
KNDy_firingRate_adult <- sepDFs$df_adult
```

## `KNDy_firingRate_juv`
```{r KNDy_firingRate_juv, fig.width=12, fig.height=18}
KNDy_firingRate_juv
```
### Control
```{r, fig.width=12, fig.height=18}
KNDy_firingRate_Juv_Con_plot
```

### PNA
```{r, fig.width=12, fig.height=18}
KNDy_firingRate_Juv_PNA_plot
```

## `KNDy_firingRate_adult`
```{r KNDy_firingRate_adult}
KNDy_firingRate_adult
```

### Control
```{r, fig.width=12, fig.height=18}
KNDy_firingRate_Adult_Con_plot
```

### PNA
```{r, fig.width=12, fig.height=18}
KNDy_firingRate_Adult_PNA_plot
```


# Averaged Firing Rate Data

This table shows the demographic variables and the average firing rate of the spontaneous period for each cell in hertz.
```{r}
#Firing Rate
KNDy_firing = KNDyDATA %>%
  filter(!is.na(SpontAvgFiring)) %>% #only take rows that are not NA for spontaneous firing rate
  select(
    SpontAvgFiring,
    all_of(demoVarsAll_quo),
    all_of(timingVars_quo),
    Quiet
  )

#Create Firing Rate Separated by Age
sepDFs <- sep_by_age(KNDy_firing)
KNDy_firing_juv <- sepDFs$df_juv
KNDy_firing_adult <- sepDFs$df_adult
```

```{r}
KNDy_firing
```

## Juveniles
```{r}
KNDy_firing_juv
```

### Jenn
```{r}
KNDy_firing_juv %>%
  filter(Who == "Jenn")
```

### Amanda
```{r}
KNDy_firing_juv %>%
  filter(Who == "Amanda")
```


## Adults

Only Amanda recorded from the adult animals
```{r}
KNDy_firing_adult
```

## Summarize Average Firing

### By Age and Treatment Group
```{r}
KNDy_summary_byGroup("SpontAvgFiring", KNDy_firing, c("GenTreatment", "AgeGroup"))
```

#### ANOVA
```{r}
#inspiration here: http://www.understandingdata.net/2017/05/11/anova-tables-in-r/
KNDyDATA_contrasts <- makeTreatandAgeContrasts(KNDyDATA)

SpontAvgFiring_model <- lm_byTreatxAge(expr(SpontAvgFiring), KNDyDATA_contrasts)

SpontAvgFiring_table <- makeANOVA_TreatAge(SpontAvgFiring_model) %>%
  kable_styling(
    font_size = 18,
    bootstrap_options = c("striped"), full_width = TRUE
  )

SpontAvgFiring_table
```

### By Age, Treatment Group, and Experimenter
```{r}
KNDy_summary_byGroup("SpontAvgFiring", KNDy_firing, c("Who", "GenTreatment", "AgeGroup"))
```

#### ANOVA
This is comparing only the juveniles by treatment group and experimenter
```{r}
KNDyDATA_juv_treatWho_contrasts <- makeTreatandWhoContrasts(KNDyDATA_juv)
SpontAvgFiring_treatWho_model <- lm_byTreatxWho(expr(SpontAvgFiring), KNDyDATA_juv_treatWho_contrasts)
SpontAvgFiring_treatWho_model <- makeANOVA_TreatWho(SpontAvgFiring_treatWho_model) %>%
  kable_styling(
    font_size = 18,
    bootstrap_options = c("striped"), full_width = TRUE
  )
SpontAvgFiring_treatWho_model
```

This is just the juveniles collapsed by experimenter, which demonstrates the difference in mean firing rate that is reflected in the ANOVA above.
```{r}
firingSum_juv_byWho <- KNDy_summary_byGroup("SpontAvgFiring", KNDy_firing_juv, c("Who"))
firingSum_juv_byWho

avgFiringRate_Jenn <- with(firingSum_juv_byWho, Mean[Who == "Jenn"])
avgFiringRate_Amanda <- with(firingSum_juv_byWho, Mean[Who == "Amanda"])
```

The average firing rate for cells that Jenn recorded is `r round(avgFiringRate_Jenn, 2)`Hz, whereas the average firing rate for the juvenile cells that Amanda recorded is `r round(avgFiringRate_Amanda, 2)`Hz.

### Jenn Recordings by Treatment Group and Age
```{r}
KNDy_summary_byGroup("SpontAvgFiring", KNDy_firing %>% filter(Who == "Jenn"), c("GenTreatment", "AgeGroup"))
```

### Amanda Recordings by Treatment Group and Age
```{r}
KNDy_summary_byGroup("SpontAvgFiring", KNDy_firing %>% filter(Who == "Amanda"), c("GenTreatment", "AgeGroup"))
```

#### ANOVA
This is the ANOVA of treatment by age for just the cells that Amanda recorded
```{r}
#inspiration here: http://www.understandingdata.net/2017/05/11/anova-tables-in-r/
KNDyDATA_AGG_contrasts <- makeTreatandAgeContrasts(KNDyDATA %>% filter(Who == "Amanda"))

SpontAvgFiring_AGG_model <- lm_byTreatxAge(expr(SpontAvgFiring), KNDyDATA_AGG_contrasts)

SpontAvgFiring_AGG_table <- makeANOVA_TreatAge(SpontAvgFiring_AGG_model) %>%
  kable_styling(
    font_size = 18,
    bootstrap_options = c("striped"), full_width = TRUE
  )

SpontAvgFiring_AGG_table
```


```{r KNDyDATA-toWorkbook}
#Store the dataframes as excel sheets
KNDyAnalysisWB = createWorkbook()

writeToWorkbook("KNDyData", KNDyDATA, KNDyAnalysisWB)
writeToWorkbook("KNDyData_juv", KNDyDATA_juv, KNDyAnalysisWB)
writeToWorkbook("KNDyData_adult", KNDyDATA_adult, KNDyAnalysisWB)
writeToWorkbook("KNDy_firingRate", KNDy_firingRate, KNDyAnalysisWB)

#Workbook saved below in the "Save Workbooks" chunk
```

